|

### 2023-07-21 journal/04-results.Rmd
added journal folder

```{r}
#| label: fig_field
#| fig.cap: "A display of the player tracking data for a play during the Las Vegas Raiders (defense, in black) versus Denver Broncos (offense, in orange) NFL game on October 17, 2021. Raiders DE Maxx Crosby is highlighted in blue. For each Raiders defender, the point size indicates their individual STRAIN value, with larger points suggesting larger STRAIN. Snapshots are captured at 1, 2, 3, and 4 seconds after the ball snap."
#| fig.width: 6.6
#| fig.height: 4.4
source(here("scripts", "01_fig_field.R"))
fig_field
```

```{r}
#| label: fig_crosby_curves
#| fig.cap: "Changes in STRAIN, velocity, and distance from the quarterback for Maxx Crosby over the course of a successful pass rush play that results in a sack. The STRAIN for other pass rushers throughout this play is also displayed."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

To illustrate our proposed metric STRAIN for pass rush evaluation, we use the same play from the Las Vegas Raiders and Denver Broncos game as mentioned in Section \ref{sec:data}.
Figure \ref{fig:fig_field} shows an updated version of Figure \ref{fig:fig_field_raw}, with the point size for each Las Vegas defender corresponding to the estimated STRAIN in the selected frames as the play progresses.
This is accompanied by Figure \ref{fig:fig_crosby_curves}, which is a line graph showing how Crosby's distance from the quarterback, velocity, and STRAIN change continuously throughout the play.

We observe that for the first two seconds, Crosby is being blocked by a Denver offensive lineman and unable to get close to the quarterback, hence the corresponding STRAIN values are virtually zero. 
Suddenly at around three seconds after the snap, the STRAIN for Crosby starts to increase after the Raiders defensive end is freed up and charges towards Bridgewater. 
At 4 seconds after the snap, Crosby's STRAIN is 2.30, which means at his current moving rate, it will take Crosby about 0.43 (1/2.30) seconds to make the distance between him and the quarterback 0 (i.e. essentially sack the quarterback).
This matches well with the final outcome of the play, as the sack takes place at the very last frame (4.4 seconds) where the estimated STRAIN for Crosby reaches its peak at 3.96.

Moreover, Figure \ref{fig:fig_crosby_curves} clearly demonstrates the interactions between the features for Maxx Crosby.
Here, a higher STRAIN generally corresponds to faster moving rate towards the quarterback.
STRAIN also increases as the distance between the pass rusher and quarterback is being reduced.
Both of these relationships suggest an overall successful pass rush by Maxx Crosby.
It is also notable that Crosby, who is credited with a sack, generates more STRAIN than other pass rushers during this play.

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this [play](https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb), Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play (as shown in Figure \ref{fig:fig_crosby_curves}) which results in a sack.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "Changes in STRAIN, velocity, and distance from the quarterback for Maxx Crosby over the course of an unsuccessful pass rush play. The STRAIN for other pass rushers throughout this play is also displayed."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions. Edge rushers (outside linebackers and defensive ends) tend to generate more STRAIN than interior rushers (defensive tackles and nose tackles). The dotted gray line represents the average STRAIN curve for all players without accounting for position."
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

```{r}
#| label: fig_outcome_curves
#| fig.cap: "Positional STRAIN curves by play outcome (sack, hit, hurry, and none)."
#| fig.width: 6.5
#| fig.height: 2.7
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

@@

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those. 
We clearly see that players tend to generate more STRAIN when a play ends in a hit, sack, or hurry, compared to no outcome.
Within the three pressure metrics, it is not surprised that a sack corresponds to the highest amount of STRAIN, followed by a hit and hurry.

## Ranking the Best Pass Rushers {#sec:strainbar}

Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size, as discussed in Section \ref{sec:defn}.
Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass rushers (nose tackles and defensive tackles) separately from edge rushers (outside linebackers and defensive ends).
Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season.
The tables also consist of the total number of hits, hurries, and sacks (determined from PFF scouting data) for each defender.

<!-- Our results show many true positives with no surprises. -->
<!-- Rashan Gary, a young rusher with huge potential, ranks first among all pass rushers according to our metric over the period of time observed. -->

Our results are mostly consistent with conventional rankings of rushers.
Notably, Myles Garrett and TJ Watt are widely recognized as top-tier edge rushers and both show up in our top edge rusher list; whereas Aaron Donald, who is undoubtedly the best interior defender in football, appears at the top of our interior rusher rankings.
Moreover, our leaderboards largely match the rankings of experts in the field.
For instance, there is considerable overlap between our lists and PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings released after the 2021 season.
This ultimately lends credibility to our proposed metric STRAIN as a measure of pass rushing effectiveness.

\begin{table}
\caption{Top 15 edge rushers (with at least 100 snaps played) according to the average STRAIN across all frames played. \label{tab:edge}}
\centering
\begin{tabular}{rlllrrrrr}
\hline
Rank & Player & Team & Position & Snaps & Hits & Hurries & Sacks & $\overline{\text{STRAIN}}$ \\
\hline
1 & Rashan Gary & GB & OLB & 176 & 10 & 25 & 5 & 2.82 \\ 
2 & Leonard Floyd & LA & OLB & 185 & 2 & 25 & 8 & 2.80 \\ 
3 & Justin Houston & BAL & OLB & 132 & 8 & 8 & 4 & 2.78 \\ 
4 & Myles Garrett & CLE & DE & 197 & 9 & 29 & 12 & 2.75 \\ 
5 & Von Miller & DEN & OLB & 145 & 4 & 21 & 5 & 2.75 \\ 
6 & T.J. Watt & PIT & OLB & 147 & 6 & 9 & 8 & 2.71 \\ 
7 & Yannick Ngakoue & LV & DE & 175 & 6 & 20 & 4 & 2.70 \\ 
8 & Alex Highsmith & PIT & OLB & 129 & 4 & 7 & 2 & 2.65 \\ 
9 & Preston Smith & GB & OLB & 124 & 4 & 8 & 2 & 2.61 \\ 
10 & Randy Gregory & DAL & DE & 134 & 7 & 19 & 5 & 2.58 \\ 
11 & Joey Bosa & LAC & OLB & 160 & 5 & 21 & 4 & 2.58 \\ 
12 & Darrell Taylor & SEA & DE & 107 & 5 & 9 & 3 & 2.57 \\ 
13 & Josh Sweat & PHI & DE & 159 & 4 & 14 & 5 & 2.57 \\ 
14 & Maxx Crosby & LV & DE & 198 & 12 & 30 & 7 & 2.56 \\ 
15 & Markus Golden & ARI & OLB & 164 & 5 & 14 & 5 & 2.50 \\ 
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Top 15 interior rushers (with at least 100 snaps played) according to the average STRAIN across all frames played. \label{tab:interior}}
\centering
\begin{tabular}{rlllrrrrr}
\hline
Rank & Player & Team & Position & Snaps & Hits & Hurries & Sacks & $\overline{\text{STRAIN}}$ \\
\hline
1 & Aaron Donald & LA & DT & 239 & 8 & 24 & 6 & 1.67 \\ 
2 & Solomon Thomas & LV & DT & 115 & 7 & 11 & 3 & 1.51 \\ 
3 & Quinton Jefferson & LV & DT & 144 & 6 & 8 & 3 & 1.46 \\ 
4 & Chris Jones & KC & DT & 139 & 3 & 18 & 3 & 1.42 \\ 
5 & DeForest Buckner & IND & DT & 198 & 4 & 18 & 4 & 1.26 \\ 
6 & Cameron Heyward & PIT & DT & 188 & 2 & 22 & 3 & 1.25 \\ 
7 & Javon Hargrave & PHI & DT & 156 & 6 & 15 & 5 & 1.24 \\ 
8 & Jerry Tillery & LAC & DT & 171 & 4 & 7 & 3 & 1.16 \\ 
9 & Ed Oliver & BUF & DT & 133 & 4 & 12 & 1 & 1.15 \\ 
10 & Osa Odighizuwa & DAL & DT & 162 & 3 & 18 & 3 & 1.13 \\ 
11 & Greg Gaines & LA & NT & 111 & 2 & 13 & 2 & 1.11 \\ 
12 & Leonard Williams & NYG & DT & 226 & 4 & 14 & 6 & 1.03 \\ 
13 & Christian Barmore & NE & DT & 166 & 5 & 17 & 1 & 1.02 \\ 
14 & Vita Vea & TB & NT & 184 & 6 & 12 & 1 & 1.01 \\ 
15 & B.J. Hill & CIN & DT & 123 & 3 & 4 & 3 & 0.96 \\ 
\hline
\end{tabular}
\end{table}

@@

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between average STRAIN and pressure rate (total hits, sacks, and hurries per snap) over the first eight weeks of the 2021 NFL season. There is a moderately strong association between average STRAIN and pressure rate ($r =0.6255$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

```{r}
#| label: fig_predictability
#| fig.cap: "Relationships between pressure rate for the last 4 weeks of the 2021 NFL season and first four weeks' pressure rate (left) and average STRAIN (right). STRAIN is more predictive ($r=0.3217$) of future pressure rate than previous pressure rate itself ($r=0.0965$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```

```{r}
#| label: fig_stability
#| fig.cap: "Relationship between average STRAIN for the last and first four weeks of the 2021 NFL season. A strong linear correlation ($r = 0.8545$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

Next, Table \ref{tab:icc} displays the intraclass correlation coefficients (ICC) for the four different groupings, describing the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the largest value, between the player and team factors, we observe the largest ICC for pass rushers, followed by the offensive and defensive teams, and the blocker.
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

@@

\begin{table}
\caption{Intraclass correlation coefficients for the multilevel model for average STRAIN. \label{tab:icc}}
\centering
\begin{tabular}{cccccc}
\hline
\text{ } & Pass rusher & Pass blocker & Defensive team & Offensive team & Residual \\ 
\hline
ICC & 0.0365 & 0.0098 & 0.0134 & 0.0143 & 0.9260 \\ 
\hline
\end{tabular}
\end{table}

@@

Aside from adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the varying intercept distributions for the top ten pass rushers for each position.
We obtain similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (defensive end), T.J. Watt (outside linebacker), Aaron Donald (defensive tackle), and Vita Vea (nose tackle) as the first-ranked pass rusher for their respective position.
Additionally, we observe different levels of variability across these top defenders, with only a subset of players having intercept distributions strictly above zero.
This is not necessarily surprising given the limited sample of data.

>>>>

<!-- ```{r} -->
<!-- #| label: fig_field -->
<!-- #| fig.cap: "A display of the player tracking data for a play during the Las Vegas Raiders (defense, in black) versus Denver Broncos (offense, in orange) NFL game on October 17, 2021. Raiders DE Maxx Crosby is highlighted in blue. For each Raiders defender, the point size indicates their individual STRAIN value, with larger points suggesting larger STRAIN. Snapshots are captured at 1, 2, 3, and 4 seconds after the ball snap." -->
<!-- #| fig.width: 6.6 -->
<!-- #| fig.height: 4.4 -->
<!-- source(here("scripts", "01_fig_field.R")) -->
<!-- fig_field -->
<!-- ``` -->

<!-- Figure \ref{fig:fig_field} shows an updated version of Figure \ref{fig:fig_field_raw}, with the point size for each Las Vegas defender corresponding to the estimated STRAIN in the selected frames as the play progresses. -->

To illustrate our proposed metric STRAIN for pass rush evaluation, we use the same play from the Las Vegas Raiders and Denver Broncos game as mentioned in Section \ref{sec:data}.
Figure \ref{fig:fig_features_combined} (left) is a line graph showing how Crosby's distance from the quarterback, velocity, and STRAIN change continuously throughout the play.
We observe that for the first two seconds, Crosby is being blocked by a Denver offensive lineman and unable to get close to the quarterback, hence the corresponding STRAIN values are virtually zero. 
Suddenly at around three seconds after the snap, the STRAIN for Crosby starts to increase after the Raiders defensive end is freed up and charges towards the QB. 
At 4 seconds after the snap, Crosby's STRAIN is 2.30, which means at his current moving rate, it will take Crosby about 0.43 (1/2.30) seconds to make the distance between him and the quarterback 0 (i.e. essentially sack the quarterback).
This matches well with the final outcome of the play, as the sack takes place at the very last frame (4.4 seconds) where the estimated STRAIN for Crosby reaches its peak at 3.96.

Moreover, we clearly see the interactions between the features for Maxx Crosby from Figure \ref{fig:fig_features_combined} (left).
Here, a higher STRAIN generally corresponds to faster moving rate towards the quarterback.
STRAIN also increases as the distance between the pass rusher and quarterback is being reduced.
Both of these relationships suggest an overall successful pass rush by Maxx Crosby.
It is also notable that Crosby, who is credited with a sack, generates more STRAIN than other pass rushers during this play.

In contrast, Figure \ref{fig:fig_features_combined} (right) shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this [play](https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb), Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play which results in a sack.

```{r}
#| label: fig_features_combined
#| fig.cap: "Changes in STRAIN, velocity, and distance from the quarterback for Maxx Crosby over the course of a successful pass rush play that results in a sack (left) and an unsuccessful pass rush play which results in a long pass attempt (right). The STRAIN for other pass rushers throughout each play is also displayed."
#| fig.width: 6.1
#| fig.height: 3.4
source(here("scripts", "15_fig_features_combined.R"))
fig_features_combined_bw
```

@@

<!-- ```{r} -->
<!-- #| label: fig_crosby_curves_unsucess -->
<!-- #| fig.cap: "Changes in STRAIN, velocity, and distance from the quarterback for Maxx Crosby over the course of an unsuccessful pass rush play. The STRAIN for other pass rushers throughout this play is also displayed." -->
<!-- #| fig.width: 4.8 -->
<!-- #| fig.height: 2.7 -->
<!-- source(here("scripts", "09_fig_play_unsuccess.R")) -->
<!-- fig_crosby_curves_unsucess -->
<!-- ``` -->

@@

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions, along with the average STRAIN curve for all players without accounting for position. Edge rushers (outside linebackers and defensive ends) tend to generate more STRAIN than interior rushers (defensive tackles and nose tackles)."
#| fig.width: 5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves_bw
```

```{r}
#| label: fig_outcome_curves
#| fig.cap: "Positional STRAIN curves by play outcome (sack, hit, hurry, and none)."
#| fig.width: 6.5
#| fig.height: 2.7
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves_bw
```

@@

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those. 
We clearly see that players tend to generate more STRAIN when a play ends in a hit, sack, or hurry, compared to no outcome.
Within the three pressure metrics, it is not surprising that a sack corresponds to the highest amount of STRAIN, followed by a hit and hurry.

<!-- ## Ranking the Best Pass Rushers {#sec:strainbar} -->

<!-- Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size, as discussed in Section \ref{sec:defn}. -->
<!-- Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass rushers (nose tackles and defensive tackles) separately from edge rushers (outside linebackers and defensive ends). -->
<!-- Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season. -->
<!-- The tables also consist of the total number of hits, hurries, and sacks (determined from PFF scouting data) for each defender. -->

<!-- <!-- Our results show many true positives with no surprises. -->
<!-- <!-- Rashan Gary, a young rusher with huge potential, ranks first among all pass rushers according to our metric over the period of time observed. -->

<!-- Our results are mostly consistent with conventional rankings of rushers. -->
<!-- Notably, Myles Garrett and TJ Watt are widely recognized as top-tier edge rushers and both show up in our top edge rusher list; whereas Aaron Donald, who is undoubtedly the best interior defender in football, appears at the top of our interior rusher rankings. -->
<!-- Moreover, our leaderboards largely match the rankings of experts in the field. -->
<!-- For instance, there is considerable overlap between our lists and PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings released after the 2021 season. -->
<!-- This ultimately lends credibility to our proposed metric STRAIN as a measure of pass rushing effectiveness. -->

<!-- \begin{table} -->
<!-- \caption{Top 15 edge rushers (with at least 100 snaps played) according to the average STRAIN across all frames played. \label{tab:edge}} -->
<!-- \centering -->
<!-- \begin{tabular}{rlllrrrrr} -->
<!-- \hline -->
<!-- Rank & Player & Team & Position & Snaps & Hits & Hurries & Sacks & $\overline{\text{STRAIN}}$ \\ -->
<!-- \hline -->
<!-- 1 & Rashan Gary & GB & OLB & 176 & 10 & 25 & 5 & 2.82 \\  -->
<!-- 2 & Leonard Floyd & LA & OLB & 185 & 2 & 25 & 8 & 2.80 \\  -->
<!-- 3 & Justin Houston & BAL & OLB & 132 & 8 & 8 & 4 & 2.78 \\  -->
<!-- 4 & Myles Garrett & CLE & DE & 197 & 9 & 29 & 12 & 2.75 \\  -->
<!-- 5 & Von Miller & DEN & OLB & 145 & 4 & 21 & 5 & 2.75 \\  -->
<!-- 6 & T.J. Watt & PIT & OLB & 147 & 6 & 9 & 8 & 2.71 \\  -->
<!-- 7 & Yannick Ngakoue & LV & DE & 175 & 6 & 20 & 4 & 2.70 \\  -->
<!-- 8 & Alex Highsmith & PIT & OLB & 129 & 4 & 7 & 2 & 2.65 \\  -->
<!-- 9 & Preston Smith & GB & OLB & 124 & 4 & 8 & 2 & 2.61 \\  -->
<!-- 10 & Randy Gregory & DAL & DE & 134 & 7 & 19 & 5 & 2.58 \\  -->
<!-- 11 & Joey Bosa & LAC & OLB & 160 & 5 & 21 & 4 & 2.58 \\  -->
<!-- 12 & Darrell Taylor & SEA & DE & 107 & 5 & 9 & 3 & 2.57 \\  -->
<!-- 13 & Josh Sweat & PHI & DE & 159 & 4 & 14 & 5 & 2.57 \\  -->
<!-- 14 & Maxx Crosby & LV & DE & 198 & 12 & 30 & 7 & 2.56 \\  -->
<!-- 15 & Markus Golden & ARI & OLB & 164 & 5 & 14 & 5 & 2.50 \\  -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->

<!-- \begin{table} -->
<!-- \caption{Top 15 interior rushers (with at least 100 snaps played) according to the average STRAIN across all frames played. \label{tab:interior}} -->
<!-- \centering -->
<!-- \begin{tabular}{rlllrrrrr} -->
<!-- \hline -->
<!-- Rank & Player & Team & Position & Snaps & Hits & Hurries & Sacks & $\overline{\text{STRAIN}}$ \\ -->
<!-- \hline -->
<!-- 1 & Aaron Donald & LA & DT & 239 & 8 & 24 & 6 & 1.67 \\  -->
<!-- 2 & Solomon Thomas & LV & DT & 115 & 7 & 11 & 3 & 1.51 \\  -->
<!-- 3 & Quinton Jefferson & LV & DT & 144 & 6 & 8 & 3 & 1.46 \\  -->
<!-- 4 & Chris Jones & KC & DT & 139 & 3 & 18 & 3 & 1.42 \\  -->
<!-- 5 & DeForest Buckner & IND & DT & 198 & 4 & 18 & 4 & 1.26 \\  -->
<!-- 6 & Cameron Heyward & PIT & DT & 188 & 2 & 22 & 3 & 1.25 \\  -->
<!-- 7 & Javon Hargrave & PHI & DT & 156 & 6 & 15 & 5 & 1.24 \\  -->
<!-- 8 & Jerry Tillery & LAC & DT & 171 & 4 & 7 & 3 & 1.16 \\  -->
<!-- 9 & Ed Oliver & BUF & DT & 133 & 4 & 12 & 1 & 1.15 \\  -->
<!-- 10 & Osa Odighizuwa & DAL & DT & 162 & 3 & 18 & 3 & 1.13 \\  -->
<!-- 11 & Greg Gaines & LA & NT & 111 & 2 & 13 & 2 & 1.11 \\  -->
<!-- 12 & Leonard Williams & NYG & DT & 226 & 4 & 14 & 6 & 1.03 \\  -->
<!-- 13 & Christian Barmore & NE & DT & 166 & 5 & 17 & 1 & 1.02 \\  -->
<!-- 14 & Vita Vea & TB & NT & 184 & 6 & 12 & 1 & 1.01 \\  -->
<!-- 15 & B.J. Hill & CIN & DT & 123 & 3 & 4 & 3 & 0.96 \\  -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->

@@

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between average STRAIN and pressure rate (total hits, sacks, and hurries per snap) over the first eight weeks of the 2021 NFL season. There is a moderately strong association between average STRAIN and pressure rate ($r =0.6255$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure_bw
```

```{r}
#| label: fig_predictability
#| fig.cap: "Relationships between pressure rate for the last 4 weeks of the 2021 NFL season and first four weeks' pressure rate (left) and average STRAIN (right). STRAIN is more predictive ($r=0.3217$) of future pressure rate than previous pressure rate itself ($r=0.0965$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability_bw
```

```{r}
#| label: fig_stability
#| fig.cap: "Relationship between average STRAIN for the last and first four weeks of the 2021 NFL season. A strong linear correlation ($r = 0.8545$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability_bw
```

@@

Next, we examine the intraclass correlation coefficients (ICC) for the four different groupings
in our multilevel model.
This descriptive statistic illustrates the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the highest value (0.9260), between the player and team factors, we observe the largest ICC for pass rushers (0.0365), followed by the offensive (0.0143) and defensive teams (0.0134), and finally the blocker (0.0098).
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

@@

<!-- \begin{table} -->
<!-- \caption{Intraclass correlation coefficients for the multilevel model for average STRAIN. \label{tab:icc}} -->
<!-- \centering -->
<!-- \begin{tabular}{cccccc} -->
<!-- \hline -->
<!-- \text{ } & Pass rusher & Pass blocker & Defensive team & Offensive team & Residual \\  -->
<!-- \hline -->
<!-- ICC & 0.0365 & 0.0098 & 0.0134 & 0.0143 & 0.9260 \\  -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->

@@

Aside from adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the varying intercept distributions for the top ten pass rushers for each position.
Our rankings based on the random intercepts are mostly consistent with conventional rankings of rushers, with Myles Garrett (defensive end), T.J. Watt (outside linebacker), Aaron Donald (defensive tackle), and Vita Vea (nose tackle) as the first-ranked pass rusher for their respective position.
Garrett and Watt are widely recognized as top-tier edge rushers, whereas Donald is undoubtedly the best interior defender in football.
Moreover, our leaderboards largely match the rankings of experts in the field.
For instance, there is considerable overlap between our lists and PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings released after the 2021 season.
This ultimately lends credibility to our proposed metric STRAIN as a measure of pass rushing effectiveness.
Additionally, we observe different levels of variability across these top defenders, with only a subset of players having intercept distributions strictly above zero.
This is not necessarily surprising given the limited sample of data.

### 2023-07-21 journal/05-discussion.Rmd
added journal folder

In this work, we have proposed STRAIN---a simple and interpretable statistic for evaluating pass rushers---with higher values corresponding to greater pass rushing ability.
STRAIN is a model-free metric which can easily be integrated into any data pipeline without much computational cost.
Visualizations of STRAIN can be useful and intuitive for coaches and broadcasters in various aspects ranging from gameplan preparation to in-game real-time play analysis.
We demonstrate that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events.
This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player tracking data can lead to the development of insightful metrics in American football. 
Through multilevel modeling, we observe that the pass rusher explains more variation in their play-level STRAIN, followed by the possession and pass rushing teams, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and defensive pressure.

Our multilevel model, however, is subject to several limitations.
We only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects.
The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true.
For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. 
This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values.
As shown in Figure \ref{fig:fig_rankings_boot}, the first- and fourth-ranked defensive ends Myles Garrett and Takkarist McKinley were teammates on the Cleveland Browns during the first eight weeks of the 2021 NFL season.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an great pass rusher.
In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach.
The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models.
We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].

>>>>

In this work, we have proposed STRAIN---a simple and interpretable statistic for evaluating pass rushers---with higher values corresponding to greater pass rushing ability.
STRAIN is a model-free metric which can easily be integrated into any data pipeline without much computational cost.
Visualizations of STRAIN can be useful and intuitive for coaches and broadcasters in various aspects ranging from gameplan preparation to in-game real-time play analysis.
We demonstrate that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events.
This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player tracking data can lead to the development of insightful metrics in American football. 
Through multilevel modeling, we observe that the pass rusher explains more variation in their play-level STRAIN, followed by the possession team and pass rushing team, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and defensive pressure.

Our multilevel model, however, is subject to several limitations.
We only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects.
The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true.
For instance, if one defender is known to be an elite pass rusher then the opposing team may focus their blocking efforts on this player. 
This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values.
As shown in Figure \ref{fig:fig_rankings_boot}, the first- and fourth-ranked defensive ends Myles Garrett and Takkarist McKinley were teammates on the Cleveland Browns during the first eight weeks of the 2021 NFL season.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is highly-regarded as an great pass rusher.
In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach.
The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models.
We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].
